---
title: "Cabbages"
author: "Mairani!"
date: "5/21/24"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  
### 
# Methods
$H_0$: there is no difference in the average vitamin c content of cabbages based on cultivation methods. 

$H_A$: There is a difference in the average vitamic c content of cabbages based on cultivation methods.
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results
vitamin c is numerical, cultivation is categorical.

### Graphical Descriptive Results
numerical-categorical so we use the numerical-Cat helper file. 

```{r}
boxplot(VitC~Cult,data=veggy)
```

Numerical is predicted by categorical.

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
The box plot shows that c52 generally has more vitamin c than c39

Vitamin c depends on cultivation method.

### Numerical Descriptive Results

```{r}
favstats(VitC~Cult,data=veggy)
```

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
The numerical summary shows that the median for c52 is 64.4. C39 is 51.0. Therefore, C52 provides more vitamin c. 


## Inferential Results

```{r}
t.test(VitC~Cult,data=veggy)
```

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
p value is 3.405e-08 which is equal to 0.000000003405. It is so small that we would reject the null hypothesis.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Cultivation method c52 has more vitamin C than method c39. Therefore, it can be concluded that there is a difference between the cultivation methods of cabbage and the null hypothesis can be rejected. The data collected proves that c52 is the better cultivation method.
